### 2021-04-13 paper.Rmd
reflect 5D cubes not 6D

The term "high-dimensional" here means Euclidean space. Figure \ref{fig:cubes} shows a way to imagine this. It shows a sequence of cube wireframes, ranging from 1D through to 6D, where beyond 2D is a linear projection of the cube. As dimension increase, a new orthogonal axis is added. For cubes, this is achieved by doubling the cube: a 2D is two 1D cubes, a 3D is two 2D cubes, and so forth.

\begin{figure*}[!h]
\centerline{\includegraphics[width=0.95\textwidth]{figures/cubes.png}}
\caption{Illustrating what is meant by "high-dimensional" in this paper, and a "linear projection". From a sequence of increasing dimension cubes, from 1D to 6D, as wireframes, it can be seen that the as dimension increase by 1, the cube doubles. (Note to Di: to change this diagram to highlight the doubling.)}
\label{fig:cubes}
\end{figure*}

>>>>

The term "high-dimensional" here means Euclidean space. Figure \ref{fig:cubes} shows a way to imagine this. It shows a sequence of cube wireframes, ranging from 1D through to 5D, where beyond 2D is a linear projection of the cube. As dimension increase, a new orthogonal axis is added. For cubes, this is achieved by doubling the cube: a 2D is two 1D cubes, a 3D is two 2D cubes, and so forth.

\begin{figure*}[!h]
\centerline{\includegraphics[width=0.95\textwidth]{figures/cubes.png}}
\caption{Illustrating what is meant by "high-dimensional" in this paper, and a "linear projection". From a sequence of increasing dimension cubes, from 1D to 5D, as wireframes, it can be seen that the as dimension increase by 1, the cube doubles. }
\label{fig:cubes}
\end{figure*}
